\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{parskip}

\hypersetup{colorlinks=true, urlcolor=black}
\pagestyle{empty}
\setlength{\parskip}{0.22em}
\renewcommand{\section}[1]{%
  \vspace{0.45em}\noindent{\bfseries #1}\\[-0.15em]
  \noindent\rule{\textwidth}{0.35pt}\vspace{0.2em}%
}

\begin{document}

\noindent
{\LARGE\bfseries EHR Media Intelligence Platform}\\[0.08em]
{\large Design Write-up}\\[0.2em]
Devansh Thakkar \enspace$\cdot$\enspace AI Full-Stack Internship Assessment \enspace$\cdot$\enspace
\href{https://github.com/DevanshThakkar19/ehr-media-intelligence}{github.com/DevanshThakkar19/ehr-media-intelligence}

\section{Problem framing}
Clinical media in Epic-like environments---labs, imaging notes, discharge summaries---rarely sits in clean structured fields. The failure mode is not ``missing AI''; it is expensive human scanning across inconsistent exports. This system treats that as a \emph{data pipeline with a thin retrieval product}: ingest synthetic heterogeneous media, normalize to a testable intermediate representation (IR), emit validated HL7 FHIR~R4 Bundles, generate orientation-only summaries, and expose sub-second semantic search in a clinician UI.

\section{Architecture}
\textbf{Ingestion $\rightarrow$ IR $\rightarrow$ FHIR $\rightarrow$ Summary $\rightarrow$ Index $\rightarrow$ UI.}
Dirty CSV/JSON/plaintext never maps straight into FHIR; cleaning lives in Pydantic models with an audit trail. FHIR~R4 emits \texttt{Patient}, \texttt{DocumentReference}, and \texttt{DiagnosticReport} as \texttt{Bundle.type=collection} (read/search, not write-back). Summaries cache on \texttt{MRN + bundle hash}. Search uses \texttt{all-MiniLM-L6-v2} + ChromaDB with resource-type and date filters. UI is Tailwind + vanilla JS over FastAPI---minimal setup, explicit API contract.

\section{Tradeoffs and why}
\begin{itemize}
\setlength{\itemsep}{0.05em}\setlength{\parsep}{0pt}\setlength{\topsep}{0.1em}
  \item \textbf{IR before FHIR.} Direct messy-to-FHIR mapping hides quality defects under coding systems. One hop buys unit-testable MRN/DOB/gender/date normalization, dedupe, and conservative identity resolution (fill missing MRN on name+DOB; never merge conflicting MRNs).
  \item \textbf{Collection Bundles, not transactions.} Assessment scope is retrieval, not Epic write-back---collection is the correct carrier for a patient's media set.
  \item \textbf{SQLite + Chroma.} \texttt{pip install} + \texttt{uvicorn} for reviewers; $\sim$50 records do not justify a service mesh.
  \item \textbf{Mock summarizer by default.} Live OpenAI/Anthropic are config flips; offline review must not depend on vendor keys.
  \item \textbf{Narrative in \texttt{description}/\texttt{conclusion}.} Searchable text over opaque Attachments at this size; production would still retain Attachments as legal source of truth.
  \item \textbf{Vanilla JS over React.} Matches the brief. A production console would still use a design-system SPA with authZ and audit.
\end{itemize}

\section{FHIR / clinical research}
FHIR~R4 reference integrity (\texttt{subject}, \texttt{encounter}); \texttt{collection} vs.\ \texttt{transaction}; LOINC document-type codes for discharge, imaging, lab, and progress notes; administrative gender vs.\ clinical sex. Summaries are labeled \textbf{orientation only}---not a decision aid---and must not invent diagnoses absent from source media.

\section{Validating AI summary quality}
\begin{enumerate}
\setlength{\itemsep}{0.05em}\setlength{\parsep}{0pt}\setlength{\topsep}{0.1em}
  \item \textbf{Contract tests:} structured sections, $\le$200 words, mandatory disclaimer, cache hit on identical \texttt{MRN + bundle hash}.
  \item \textbf{Faithfulness spot-checks} (CHF/BNP, nodule, appendicitis US, CAP, allergy): claims must appear in source text; temperature 0.2 + anti-fabrication prompt with a live key.
  \item \textbf{Retrieval sanity:} ``elevated BNP failure'' ranks true media (e.g., BMP \& BNP) above twin FHIR projections and unrelated summaries.
\end{enumerate}

\section{What I would ship next}
US Core + real \texttt{Encounter} resources; PDF/OCR ingest; automated faithfulness (claim $\leftrightarrow$ source-span); hybrid BM25+vector for MRN/accession exact match; AuthN/Z and immutable audit for a hospital VPC---the gap between a strong demo and something behind a BAA.

\end{document}
